---
title:           Label Images Helper
author:          Dennis Wollersheim 
date:            11.10.2018
linkcolor:       cyan
citecolor:       grey
output:
  pdf_document:
    highlight:   zenburn
---
```{r load_data}

source('lib/loadFunctions.R')
source('lib/loadData.R')

#df_motion %>% View  

```


```{r feature_engineeering}
df_motion

df_category

basedir = '/mnt/pivideo/mnt/video/2018/11/'
embeddir = paste0( basedir, '/embed/' )
imagedir = paste0( basedir, '/images/02/' )

list.files(imagedir, pattern="*[0-9].jpg", full.names=TRUE)  %>%
data.frame( image=., stringsAsFactors=FALSE) %>%
  mutate( key =str_replace( filenames, '.*/(.*).jpg','\\1')) %>%
  as_tibble() %>% 
  { . } -> filenames

l

df_motion %>%
  group_by( text_event ) %>%
  mutate( event_frame = row_number(),
          second = ts - min( ts),
          duration= as.hms( max( ts ) - min( ts )) 
    ) %>%
  group_by( text_event, second ) %>%
  mutate( ms = frame / max( frame ), 
         et = second + ms ) %>%
  ungroup() %>% 
  { . } -> df_motion

df_motion %>%
  mutate( event_time = substring( text_event, 9,14),  
  period = ifelse(event_time > '0630' & event_time < '1930', 'day','night')) %>%
  group_by( text_event, event_time, period) %>%
  filter( file_type==4) %>%
  summarise(  clip_time = min(event_time_stamp), 
              duration= as.hms( max( ts ) - min( ts )) ,
              nframe = n(),
              max_pix = max(numpixel), 
              max_ratio = max( motion_height / motion_width ), 
              max_height = max( motion_height ),
              max_width = max( motion_width ),
              max_x = max( motion_X), 
              max_y = max( motion_Y) ,
              min_pix = min(numpixel), 
              min_ratio = min( motion_height / motion_width ), 
              min_height = min( motion_height ),
              min_width = min( motion_width ),
              min_x = min( motion_X), 
              min_y = min( motion_Y) ,
              mean_pix = mean(numpixel), 
              mean_ratio = mean( motion_height / motion_width ), 
              mean_height = mean( motion_height ),
              mean_width = mean( motion_width ),
              mean_x = mean( motion_X), 
              mean_y = mean( motion_Y) ,
              sd_pixel = sd(numpixel, na.rm=TRUE), 
              sd_ratio = sd( motion_height / motion_width , na.rm=TRUE), 
              sd_height = sd( motion_height ),
              sd_width = sd( motion_width ),
              sd_x = sd( motion_X), 
              sd_y = sd( motion_Y) ,
              tb=max( motion_X ) - min( motion_X ),
              ss=max( motion_Y ) - min( motion_Y )
            ) %>% 
  ungroup() %>%
  left_join( df_category, by='text_event' ) %>%
  { . } -> df_text_event

df_motion %>%
  filter( file_type==8 ) %>%
  select( text_event, filename )  %>% 
  { . } -> df_movie 

df_text_event %>%
  ggplot( aes( x=max_x )) + geom_histogram()

df_text_event %>%
  count( max_x, sort=TRUE) 


df_text_event %>%
  filter( period == 'day' & 
         min_x <100 & 
         max_x > 250 & 
         duration < 20 &
         is.na( class )) %>%
inner_join( df_movie ) %>%
mutate( te = paste( 
                  substring( text_event, 1,4 ), 
                  substring( text_event, 5,6 ), 
                  substring( text_event, 7,8 ), 
                  substring( text_event, 9,10)
                  ),
      filename = paste0( '/mnt/pivideo/', filename ),
      text_event = paste0( "'", text_event )
       ) %>%
  select( text_event, te, filename, duration, class ) %>%
  arrange( duration ) %>%
  write.csv( 'data/toclassify.csv', row.names=FALSE)

df_motion %>% 
  filter( file_type==4) %>%
  group_by(text_event ) %>% 
  do(model = lm(event_frame ~ motion_X, data = .)) %>% 
  rowwise() %>% 
  tidy(model) %>%
  filter( term=='motion_X') %>%
  select(-term) %>%
  mutate( direction_X = ifelse( estimate<0, 'left', 'right' )) %>% 
  mutate( speed_X = abs(estimate)) %>% 
  { . } -> motion_X

df_motion %>% 
  filter( file_type==4) %>%
  group_by(text_event ) %>% 
  do(model = lm(event_frame ~ motion_Y, data = .)) %>% 
  rowwise() %>% 
  tidy(model) %>%
  filter( term=='motion_Y') %>%
  select(-term) %>%
  mutate( direction_Y = ifelse( estimate<0, 'up', 'down' )) %>% 
  mutate( speed_Y = abs(estimate)) %>% 
  { . } -> motion_Y

df_text_event %>%
  left_join( motion_X ) %>%
  rename( inconsistent_X=std.error ) %>%
  select( -estimate, -statistic, -p.value ) %>% 
  { . } -> df_text_event

df_text_event %>%
  left_join( motion_Y ) %>%
  rename( inconsistent_Y=std.error ) %>%
  select( -estimate, -statistic, -p.value ) %>% 
  { . } -> df_text_event








```{r pairs}

# events remaining to categorise
df_category %>% distinct( text_event )

df_category %>%
  right_join( df_text_event ) %>%
  select( clip_time, text_event, duration, class ) %>%
  filter( is.na( class) ) %>% 
  select (text_event ) 


# all pairs of variables 
df_text_event %>%
  inner_join( df_category ) %>%
  ggpairs( columns=c(5,8:14), 
          mapping=aes( color=class),
          legend=c(1,1)
          ) 

  # all pairs of variables 
  df_text_event %>%
    inner_join( df_category ) %>%
    ggpairs( columns=c(5, 8, 15:20), 
            mapping=aes( color=class),
            legend=c(1,1)
            ) 

    # all pairs of variables 
    df_text_event %>%
      inner_join( df_category ) %>%
      ggpairs( columns=c(8,18,19,21:25 ), 
              mapping=aes( color=class),
              legend=c(1,1)
              ) 

      # all pairs of variables 
      df_text_event %>%
        inner_join( df_category ) %>%
        ggpairs( columns=c(8,18,26:31 ), 
                mapping=aes( color=class),
                legend=c(1,1)
                ) 

# all pairs of variables 
df_text_event %>%
  inner_join( df_category ) %>%
  ggpairs( columns=c(8,18,32:36 ), 
          mapping=aes( color=class),
          legend=c(1,1)
          ) 


# all pairs of variables 
df_text_event %>%
  mutate( duration=as.numeric( duration)) %>%
  drop_na( ) %>%
  ggpairs() %>% 
  ggsave( '/tmp/toview.png', ., width=20, height=20, units='in', dpi=600)

```
```{r prediction}
library( randomForest)
library(caret)

df_text_event %>%
  inner_join( df_category ) %>%
  select( nframe, 
         starts_with('max'), 
         starts_with('min'), 
         starts_with('mean'), 
  "tb", "ss", "inconsistent_X", "direction_X", "speed_X", "inconsistent_Y",
  "direction_Y", "speed_Y", class) %>% 
  drop_na() %>%
  filter( class %in% c('c', 'p')) %>%
  mutate( direction_X = as.factor( direction_X),
         direction_Y = as.factor( direction_Y),
         class=as.factor(class)) %>%
  { . } -> df

split=0.80
inTrain <- createDataPartition(y = df$class, p = split, list = FALSE)
training <- df[inTrain,]
testing <- df[-inTrain,]

  randomForest( y=training$class, 
               x=dplyr::select( training, -class ),
               ytest=testing$class,
               xtest = dplyr::select( testing, -class ),
                 ntree=1000 ) %>% 
  { . } -> fit

summary(fit)
plot(fit)
fit$confusion

my=as.factor( df$class )
mx = df %>% select( -class )
randomForest( y=my, x= mx, ntree=100000)  -> model
summary(model)


plot(model)
model$confusion

library(nnet ) 

df %>% 
  select( -class ) %>%
  names() %>%
  paste0( collapse='+') %>%
  formula( paste0( 'class~', . ), data=df)

fit=multinom( class ~ nframe+max_pix+max_ratio+max_height+max_width+max_x+max_y+min_pix+min_ratio+min_height+min_width+min_x+min_y+mean_pix+mean_ratio+mean_height+mean_width+mean_x+mean_y+tb+ss+inconsistent_X+direction_X+speed_X+inconsistent_Y+direction_Y+speed_Y, data=df )

fit


fit=glm( class ~ max_pix+max_pix+min_ratio+mean_pix+mean_ratio+mean_height+tb, family=binomial, data=training )
summary( fit )

#fit=glm( class ~ max_ratio+max_height+max_width+min_pix+min_ratio+min_height+min_width+mean_pix+mean_ratio+mean_height+mean_width+mean_x+mean_y+tb+ss+inconsistent_X+direction_X+speed_X+inconsistent_Y+direction_Y+speed_Y,family=binomial, data=df )

fit=glm( class ~ mean_pix + max_width+min_pix+min_ratio+min_height+min_width+mean_pix+mean_ratio+mean_height+mean_width+mean_x+mean_y+tb+ss+inconsistent_X+speed_X+inconsistent_Y+direction_Y+speed_Y,family=binomial, data=training )
summary( fit )
#
car::vif( fit )

testing %>%
  dplyr::select( -class ) %>%
  predict( fit, . ) %>% 
  { . } -> predictions

y_test <- testing[,'class']
# summarize results
confusionMatrix(predictions, y_test)



as.factor( pdata>.5 )


# naive bayes
# load the libraries
library(klaR)

# train a naive bayes model
model=NaiveBayes( class ~ mean_pix + max_width+min_pix+min_ratio+min_height+min_width+mean_pix+mean_ratio+mean_height+mean_width+mean_x+mean_y+tb+ss+inconsistent_X+speed_X+inconsistent_Y+direction_Y+speed_Y,family=binomial, data=training )
# make predictions
x_test <- testing[,1:4]
y_test <- testing[,5]
predictions <- predict(model, x_test)
# summarize results
confusionMatrix(predictions$class, y_test)
```


# explore ranges 
```{r}

df_motion %>%
  distinct( text_event, duration ) %>%
  ggplot( aes( duration ) ) + geom_histogram()


```


# explore directionality
```{r}

df_motion %>%
  filter( duration<15) %>%
  filter( file_type==4) %>%
  ggplot( aes(event_frame, motion_X, group=text_event )) +
  geom_line() + 
  facet_wrap( ~duration, scales='free_x' )

df_motion %>%
  filter( duration<15) %>%
  filter( file_type==4) %>%
  ggplot( aes(second, motion_X, group=text_event )) +
         geom_line() + 
         facet_wrap( ~duration, scales='free_x' )


df_motion %>% 
  filter( file_type==4) %>%
  group_by(text_event ) %>% 
  do(model = lm(event_frame ~ motion_X, data = .)) %>% 
  rowwise() %>% 
  tidy(model) %>%
  filter( term=="motion_X" ) %>%
  mutate( direction = ifelse( estimate<0, 'down', 'up' )) %>% 
  { . } -> motion_X
  

df_motion %>%
  inner_join( motion_X ) %>%
  filter( duration<15) %>%
  filter( file_type==4) %>%
  ggplot( aes(event_frame, motion_X, group=text_event, color=direction )) +
  geom_line() + 
  facet_wrap( ~duration, scales='free_x' )



df_motion %>%
  group_by( text_event ) %>%

```


